Properties of coronal Fourier power spectra and their implications for coronal seismology and solar atmospheric heating.

### 2014-05-09 tex/paper1/paper1.tex
edits to the paper

\begin{abstract}
The Fourier power spectra of regions of the solar corona are
investigated using AIA 171\AA\ and 193\AA\ data.  It is shown that the
Fourier power spectra in all the regions show a power law behaviour
approximately.  This suggests that in many parts of the corona a
background model consisting of white noise and a trend cannot be
assumed when analyzing for the presence of oscillations in the corona.
Further, it is shown that the observed power law power spectrum can be
formed by summing a distribution of exponentially decaying emission
events along the line of sight.  This is consistent with the notion
that the solar atmosphere is heated everywhere by small energy
deposition events.
\end{abstract}

@@

Consider the emission from a single pixel, $I(t)$.  The Fourier power
spectrum for this emission was calculated as follows.  First, the
time-series was normalized by calculating $(I(t) - \langle I(t)
\rangle)/\langle I(t) \rangle$. Secondly, the normalized time-series
was apodized using the Hanning window, reducing ringing effects in the
power spectrum.  Figures \ref{fig:compare171193} show example power
spectra, plotted using a log-log scale, from a single location inside
each of the regions shown in Figure \ref{fig:loc171193}.  The shape of
the power spectra indicate that the Fourier power approximately
follows a power law at lower frequencies, and flattens out at higher
frequencies.

@@

\begin{figure}
\plottwo{shutdownfun3_6hr_disk_1.5_193_loopfootpoints.hanning.relative.power_spectra_distributions.eps}{shutdownfun3_6hr_disk_1.5_193_moss.hanning.relative.power_spectra_distributions.eps}
\plottwo{shutdownfun3_6hr_disk_1.5_193_qs.hanning.relative.power_spectra_distributions.eps}{shutdownfun3_6hr_disk_1.5_193_sunspot.hanning.relative.power_spectra_distributions.eps}
\caption{Distribution of Fourier power at some sample frequencies (see
  also Figure \ref{fig:dist171} for the corresponding AIA
  171\AA\ plots.)}
\label{fig:dist193}
\end{figure}
Figures \ref{fig:dist171} and \ref{fig:dist193} show the distributions
of the logarithm of the Fourier power for a small number of
frequencies, for all the pixels in each region.  The distributions all
follow a normal distribution approximately.  This indicates that the
power in each each at each frequency is approximately log-normally
distributed.  This observation guides the choice of how to average the
power spectrum over each of the selected region.  Since the Fourier
power is log-normally distributed, the arithmetic mean of the Fourier
power is biased by the very largest powers.  Since the logarithm of
the Fourier power is approximately Gaussian-distributed, the mean
value is a better representation of the range of values in the data.
Hence the mean of the logarithm of the Fourier power is used to
describe the mean Fourier power spectrum of each region (note that
this is also equivalent to the geometric mean of the Fourier power.)

@@

\begin{deluxetable}{cccccccc}
\tabletypesize{\scriptsize}
\tablecolumns{5}
\tablewidth{0pt}
\tablecaption{Parameter values and uncertainty estimates derived for
    model \protect$M_{2}$.\label{tab:parameters}}
\tablehead{
\colhead{Region} & 
\colhead{Waveband}    & 
\multicolumn{3}{c}{power law} & \multicolumn{3}{c}{lognormal} \\
\colhead{}          & 
\colhead{}          & 
\colhead{$\log_{10}A$}          & 
\colhead{$n$}      & 
\colhead{$\log_{10}C$}      &
\colhead{$\log_{10}\alpha$} &
\colhead{$\beta$}      &
\colhead{$\sigma$}\\
\colhead{}          & 
\colhead{}          & 
\colhead{}          & 
\colhead{}      & 
\colhead{}      &
\colhead{} &
\colhead{(mHz)}      &
\colhead{(decades of frequency)}\\
}
\startdata
loop footpoints & 171\AA  & $0.65^{+0.02}_{-0.02}$  &$2.27^{+0.02}_{-0.02}$  & $-4.15^{+0.00}_{-0.00}$  & $-2.16^{+0.12}_{-0.11}$ & $0.64^{+0.10}_{-0.10}$  & $0.33^{+0.02}_{-0.02}$  \\
                & 193\AA  & $0.21^{+0.02}_{-0.02}$  & $2.27^{+0.03}_{-0.03}$ & $-4.26^{+0.00}_{-0.00}$  & $-2.24^{+0.09}_{-0.10}$ & $0.37^{+0.06}_{-0.04}$  & $0.40^{+0.01}_{-0.02}$  \\
                & & & & & & & \\

@@

The (geometric) mean Fourier power spectra are shown in Figures
\ref{fig:fit171} and \ref{fig:fit193}, for each of the physical
regions considered.  It is clear that, in general, the Fourier power
spectra exhibit power-law like characteristics.  The results for the
quiet Sun, loop footpoints and sunspot regions suggest a power-law
power spectrum.  This can be modeled as
\begin{equation}
\label{eqn:pwrlaw}
\mbox{Model $M_{1}$}: P_{1}(\nu) = A\nu^{-n} + C,
\end{equation}
where $\nu$ is the normalized frequency, $A>0$ is a proportionality
constant and $n>0$ is the power law index.  The quantity $C>0$ models
the high-frequency / low power end of the spectrum where the detection
properties of the detector apparatus are assumed to dominate the
observations.

@@

\section{Discussion}
The presence of a power law Fourier spectrum in coronal emission poses
questions about how that emission is formed.  The power law power
spectrum also has implications for the detection of narrow frequency
band oscillations against such a background emission, which is the
purview of coronal seismology.  We discuss these two topics in the
sections below.

\subsection{Effect of background power spectrum assumptions on the
  detection of oscillatory power}
\label{ssec:corseis}

Section \ref{sec:anal} demonstrates the presence of a red
noise-like signal in two of the most commonly used wavebands for
coronal seismology, SDO-AIA 171\AA\ and 193\AA.  The observed spectra
generally show a power law-like behavior at time-scales of interest in
coronal seismology, and longer.  Within the confines of the models we
have chosen, coronal moss regions show the largest contribution from a
non-power law power spectrum source over a relatively limited range of
frequencies.  The frequencies at which the lognormal contribution is
larger than the underlying power-law distribution could be used to
define an average frequency range within which the majority
contribution to the overall Fourier power is not associated with the
underlying power-law distribution.  However, the \Fps\ in this range
would still have to analyzed using both the power-law and lognormal
contributions to the overall power, and better estimates to the
power-law parameters will be obtained if the full frequency range of
the observations are used.

The presence of a non-power law contribution to the \Fps\ does not
change the fact that the background emission is essentially power-law
like.  For the frequencies that have been of interest in coronal
seismology, the background power spectrum is therefore scale free on
average.  If there is no time-scale that can be used to remove a
background trend, then the time-series has to be analyzed without this
processing step.  However, a lack of awareness of the background
red-noise nature of the emission can cause problems in attempting to
analyze for the presence of narrow frequency band oscillations, as the
following example demonstrates.

\begin{figure}
\epsscale{.80}
\plotone{white_red_compare.eps}
\caption{Comparison of the effect of assuming a white or red noise
  background on the detection of an oscillatory signal for simulated
  time-series.  Plot (a) shows the simulated time-series, generated
  from a power spectrum \protect$P(f)\approx f^{-1.77}$ and no
  explicit oscillation included.  Plot (b) shows the wavelet power
  spectrum with the cone-of-influence (shaded area) and regions above
  the 95\% confidence level, assuming a white-noise (Gaussian)
 background .  Plot (c) shows the global wavelet power spectrum for
  this wavelet transform.  Plots (d) and (e) are the same as plots (b)
  and (c) under the assumption of a red-noise background.}
\label{fig:comparison}
\end{figure}

Figure \ref{fig:comparison} shows how a red-noise power spectrum can
be mistakenly thought to contain an oscillatory signal.  The time
series (Figure \ref{fig:comparison}(a)) is constructed from a power
spectrum $P(f)\approx f^{-1.77}$ with no explicit oscillatory content,
following the construction procedure of \cite{2010MNRAS.402..307V}.
Figure \ref{fig:comparison}(b) shows that the assumption of a
white-noise background and a 95\% confidence level leads to the
positive detection of significant oscillatory power in this time
series. Figure \ref{fig:comparison}(c) shows that the assumption of a
red-noise background with the same confidence level significantly
reduces the area for which a detection may be claimed.  This simulated
data, along with the results of Section \ref{sec:anal}, suggest that
when examining the wavelet transforms of time-series for wave packets,
a background red-noise power spectrum should be assumed, along with
higher confidence levels, in order to minimize the effects of
mistakenly identifying random variations in the background power
spectrum as evidence for an oscillatory signal.

Even this approach to identifying oscillatory power is not quite
complete, as it simply rejects the null hypothesis that the power
spectrum can be adequately explained by a red-noise power spectrum.
Model comparison techniques similar to that described in Section
\ref{sec:anal} is required to prefer a model with oscillatory content
over one without. The difficulty in finding narrow-band features in
Fourier power spectra against a red-noise background power spectrum
has been recognized by \cite{2010MNRAS.402..307V} in the study of
XMM-Newton observations of highly variable Seyfert 1 galaxies.
\cite{2010MNRAS.402..307V} presents a model fitting and comparison
technique is directly applicable to the search for oscillatory power
in coronal time-series.

@@

Figure \ref{fig:compare171193} shows that time series from individual
pixels have power-law like power spectra.  This has implications for
the design of automated oscillation detection algorithms.  Such an
algorithm must take into account the nature of the power spectrum.
The power-law power spectrum itself lacks an easily definable
time-scale at or below which a background trend can be defined.
Automated detection algorithms that rely on background trend
subtraction such as \cite{2010SoPh..264..403I} must therefore look to
other reasons for to justify a time-scale.

@@

All the automated detection algorithms described above attempt to find
individual pixels that are obviously oscillating at some frequency,
using the strength of the oscillation at that frequency (compared to
some assumption of the background) as the key quantity to measure.
These pixels are then clumped together and the quality of the signal
is then assessed.  Detection algorithms based on {\it wave coherence},
such as \cite{2008SoPh..252..321M}, implement wave detection through
finding spatially contiguous regions of the corona which are coherent
in a given frequency range.  The frequency range searched is based on
previous experience.  Oscillations that are detected propagating along
loops are often found by considering distance-time plots
\citep{2000AA...355L..23D, 2003AA...404L...1K} and looking for
alternating brightening/darkening in those plots as a indicator of a
propagating wave.  This is essentially a coherence-based approach that
involves an implicit assessment of the likelihood that an oscillation
has been detected.  The basis of the assessment is a judgement that a
signal is seen in multiple contiguous pixels.  However, the results of
Section \ref{sec:anal} suggest that each pixel in these plots has a
red-noise background power spectrum: the discussion of Section
\ref{ssec:corseis} therefore suggests that the significance of any
claimed oscillation is much reduced.

\subsection{``Excess'' emission}\label{ssec:excess}
The models fits of Section \ref{sec:anal} indicate that equation
\ref{eqn:pwrlaw} is preferred over equation \ref{eqn:pwrlawbump} as
the superior description of the observed Fourier power spectrum. The
moss region shows the greatest contribution from the lognormal
distribution $G(\nu)$ over the background power law.
\cite{2005ApJ...624L..61D} show that it is possible to leak
oscillatory power from lower in the atmosphere to the upper reaches of
the atmosphere through the simple expedient of tilting the field line.
This changes the acoustic cutoff frequency and so allows wave energy
to propagate up in to the upper atmosphere.  If spectral model $M_{2}$
represents conditions in the solar atmosphere, then it should be
possible to infer a distribution of field line angles with the solar
surface using \cite{2005ApJ...624L..61D} and the observed power
distribution $G(\nu)$.  This would constrain the distribution of field
line angles in the lower atmosphere in different regions of the solar
surface.

\subsection{Nature of the power law power spectrum}\label{ssec:nplps}
The first contribution to both models $P_{0}$ and $P_{i}$ is a
red-noise like power spectrum.  It is present in both wavebands
studied and in all the regions, and so parsimony suggests that the
mechanism of its creation is both similar and ubiquitous in all parts
of the solar atmosphere.  We hypothesize that the \PL\ \PS\ is due to
the sum of a distribution of a large number of energy deposition
events having different energies. \cite{2011soca.book.....A} describes
how a \PL\ \PS\ may obtained from such a distribution, and that
argument is outlined below.

Each energy deposition event is modeled as an exponentially decaying
function of time $t$
\begin{equation}
\label{eqn:expdecay}
f(t) = \frac{E}{T}\exp\left(-\frac{t}{T}\right),
\end{equation}
for some timescale $T$ and energy $E$.  The corresponding \Fps\ is
\begin{equation}
\label{eqn:ftexpdecay}
P(\nu) = \frac{E}{1 + (2\pi \nu T)^{2}}.
\end{equation}
The total \Fps\ along the line of sight is given by
\begin{equation}
\label{eqn:sumftexpdecay}
P_{T}(\nu) = \sum_{T}N(T)P_{T}(\nu)
\end{equation}
where $N(T)$ is the distribution of time-scales for all the events
along the line of sight.  Further, if the number of events of a given
energy $E$ is assumed to be
\begin{equation}
\label{eqn:energydistrib}
N(E) \propto E^{-\alpha_{E}}
\end{equation}
and the energy in each event depends on its time scale $T$ such that
\begin{equation}
\label{eqn:energytime}
E \propto T^{1+\gamma}
\end{equation}
then it can be shown that the observed power spectrum can be
approximated by
\begin{equation}
\label{eqn:finalfps}
P(\nu) \propto \nu^{(2-\alpha_{E})(1+\gamma)}.
\end{equation}

This derivation shows it is possible to generate \PL\ power spectra
using swarms of statistically similar events.  The detailed
application of this model of the observed background \PL\ power
spectra will depend strongly on three factors that influence the
observation.  Firstly, the distribution of events along the line of
sight and their temporal dependence (expressed through the parameters
$\alpha_{E}$ and $\gamma$ in Equation \ref{eqn:energydistrib}) have
strong effects on the observed \Fps.  Secondly, the energy radiated as
a function of the energy deposited in each event and the existing
plasma properties must be consistently modeled.  This is required to
understand how much radiation at each wavelength is emitted from the
plasma.  Finally, the AIA instrument filters the emitted radiation,
and this too must be modeled in order to understand the observed \Fps.
These three features must be modeled in order to test the hypothesis
that ubiquitous energy deposition events are the root cause of the
observed power-law like behavior of the Fourier power spectra.

@@

Time series of AIA 171\AA\ and 193\AA images show approximately power
law like properties over all regions of the solar surface.  Detecting
narrow band oscillatory power should take in to account the presence
of the power-law like power spectrum.  The power spectra have been
modelled using three components: a power-law power spectrum, a
lognormal component, and a constant background.  It is hypothesized
that the power-law component is due to the sum along the line of sight
of a large number of statistically similar energy deposition events.
It is also hypothesized that the lognormal component is due to the
channeling of oscillatory power from lower to higher levels of the
solar atmosphere.

@@

The estimated
error in the estimated error is
\begin{equation}
\sqrt{\hat{\sigma^{2}}}/\sqrt{N}
\label{eqn:errorsigmamean}
\end{equation}

@@

\bibliography{references}
\end{document}
However, other more complex models are certainly possible.  For
example, \cite{1993ASPC...42..111H} modelled the background
chromospheric Fourier power spectrum of a series of Ca-II K-line
images using a 19-parameter fit consisting of a constant background,
three components of the form
\begin{equation}
\label{eqn:harvey1}
P(\nu) \propto \frac{1}{1 + (2\pi \nu T_{0})^{b}}.
\end{equation}
and two components of the form
\begin{equation}
\label{eqn:harvey2}
P(\nu) \propto
\left(
\frac{\nu}{\nu_{0}}
\right)^{c}
\left(
\frac{\Gamma^{2}}{(\nu-\nu_{0})^{2} + \Gamma^{2}}
\right)^{b}.
\end{equation}

Finally, only two models of the Fourier power spectrum have been
considered.  The choice of equation \ref{eqn:pwrlaw} is motivated by
the observations of all four regions considered.  Equation
\ref{eqn:pwrlawbump} was motivated by previous observations of
oscillatory content in the solar atmosphere.  Equation
\ref{eqn:pwrlawbump} is shown to be the preferred model in all cases.

>>>>

\begin{abstract}
The Fourier power spectra of regions of the solar corona are
investigated using AIA 171\AA\ and 193\AA\ data.  It is shown that the
Fourier power spectra in all the regions show a \PL\ behaviour
approximately.  This suggests that in many parts of the corona a
background model consisting of white noise and a trend cannot be
assumed when analyzing for the presence of oscillations in the corona.
Further, it is shown that the observed \PL\ \PS\ can be
formed by summing a distribution of exponentially decaying emission
events along the line of sight.  This is consistent with the notion
that the solar atmosphere is heated everywhere by small energy
deposition events.
\end{abstract}

@@

Consider the emission from a single pixel, $I(t)$.  The Fourier power
spectrum for this emission was calculated as follows.  First, the
time-series was normalized by calculating $(I(t) - \langle I(t)
\rangle)/\langle I(t) \rangle$. Secondly, the normalized time-series
was apodized using the Hanning window, reducing ringing effects in the
\PS.  Figures \ref{fig:compare171193} show example power
spectra, plotted using a log-log scale, from a single location inside
each of the regions shown in Figure \ref{fig:loc171193}.  The shape of
the power spectra indicate that the Fourier power approximately
follows a \PL\ at lower frequencies, and flattens out at higher
frequencies.

@@

\begin{figure}
\plottwo{shutdownfun3_6hr_disk_1.5_193_loopfootpoints.hanning.relative.power_spectra_distributions.eps}{shutdownfun3_6hr_disk_1.5_193_moss.hanning.relative.power_spectra_distributions.eps}
\plottwo{shutdownfun3_6hr_disk_1.5_193_qs.hanning.relative.power_spectra_distributions.eps}{shutdownfun3_6hr_disk_1.5_193_sunspot.hanning.relative.power_spectra_distributions.eps}
\caption{Distribution of Fourier power at some sample frequencies (see
  also Figure \ref{fig:dist171} for the corresponding AIA
  171\AA\ plots.)}
\label{fig:dist193}
\end{figure}
Figures \ref{fig:dist171} and \ref{fig:dist193} show the distributions
of the logarithm of the Fourier power for a small number of
frequencies, for all the pixels in each region.  The distributions all
follow a normal distribution approximately.  This indicates that the
power in each each at each frequency is approximately log-normally
distributed.  This observation guides the choice of how to average the
\PS\ over each of the selected region.  Since the Fourier
power is log-normally distributed, the arithmetic mean of the Fourier
power is biased by the very largest powers.  Since the logarithm of
the Fourier power is approximately Gaussian-distributed, the mean
value is a better representation of the range of values in the data.
Hence the mean of the logarithm of the Fourier power is used to
describe the mean \Fps\ of each region (note that
this is also equivalent to the geometric mean of the Fourier power.)

@@

\begin{deluxetable}{cccccccc}
\tabletypesize{\scriptsize}
\tablecolumns{5}
\tablewidth{0pt}
\tablecaption{Parameter values and uncertainty estimates derived for
    model \protect$M_{2}$.\label{tab:parameters}}
\tablehead{
\colhead{Region} & 
\colhead{Waveband}    & 
\multicolumn{3}{c}{\PL} & \multicolumn{3}{c}{lognormal} \\
\colhead{}          & 
\colhead{}          & 
\colhead{$\log_{10}A$}          & 
\colhead{$n$}      & 
\colhead{$\log_{10}C$}      &
\colhead{$\log_{10}\alpha$} &
\colhead{$\beta$}      &
\colhead{$\sigma$}\\
\colhead{}          & 
\colhead{}          & 
\colhead{}          & 
\colhead{}      & 
\colhead{}      &
\colhead{} &
\colhead{(mHz)}      &
\colhead{(decades of frequency)}\\
}
\startdata
loop footpoints & 171\AA  & $0.65^{+0.02}_{-0.02}$  &$2.27^{+0.02}_{-0.02}$  & $-4.15^{+0.00}_{-0.00}$  & $-2.16^{+0.12}_{-0.11}$ & $0.64^{+0.10}_{-0.10}$  & $0.33^{+0.02}_{-0.02}$  \\
                & 193\AA  & $0.21^{+0.02}_{-0.02}$  & $2.27^{+0.03}_{-0.03}$ & $-4.26^{+0.00}_{-0.00}$  & $-2.24^{+0.09}_{-0.10}$ & $0.37^{+0.06}_{-0.04}$  & $0.40^{+0.01}_{-0.02}$  \\
                & & & & & & & \\

@@

The (geometric) mean Fourier power spectra are shown in Figures
\ref{fig:fit171} and \ref{fig:fit193}, for each of the physical
regions considered.  It is clear that, in general, the Fourier power
spectra exhibit power-law like characteristics.  The results for the
quiet Sun, loop footpoints and sunspot regions suggest a \PL\ \PS.
This can be modeled as
\begin{equation}
\label{eqn:pwrlaw}
\mbox{Model $M_{1}$}: P_{1}(\nu) = A\nu^{-n} + C,
\end{equation}
where $\nu$ is the normalized frequency, $A>0$ is a proportionality
constant and $n>0$ is the \PL\ index.  The quantity $C>0$ models
the high-frequency / low power end of the spectrum where the detection
properties of the detector apparatus are assumed to dominate the
observations.

@@

\section{Discussion}
The presence of a \PL\ Fourier spectrum in coronal emission poses
questions about how that emission is formed.  The \PL\ \PS\ also has
implications for the detection of narrow frequency band oscillations
against such a background emission, which is the purview of coronal
seismology.  We discuss these two topics in the sections below.

\subsection{Effect of background \PS\ assumptions on the
  detection of oscillatory power}
\label{ssec:corseis}

Section \ref{sec:anal} demonstrates the presence of a red
noise-like signal in two of the most commonly used wavebands for
coronal seismology, SDO-AIA 171\AA\ and 193\AA.  The observed spectra
generally show a \PL-like behavior at time-scales of interest in
coronal seismology, and longer.  Within the confines of the models we
have chosen, coronal moss regions show the largest contribution from a
non \PL\ \PS\ source over a relatively limited range of
frequencies.  The frequencies at which the lognormal contribution is
larger than the underlying power-law distribution could be used to
define an average frequency range within which the majority
contribution to the overall Fourier power is not associated with the
underlying power-law distribution.  However, the \Fps\ in this range
would still have to analyzed using both the power-law and lognormal
contributions to the overall power, and better estimates to the
power-law parameters will be obtained if the full frequency range of
the observations are used.

The presence of a non \PL\ contribution to the \Fps\ does not change
the fact that the background emission is essentially power-law like.
For the frequencies that have been of interest in coronal seismology,
the background \PS\ is therefore scale free on average.  If there is
no time-scale that can be used to remove a background trend, then the
time-series has to be analyzed without this processing step.  However,
a lack of awareness of the background red-noise nature of the emission
can cause problems in attempting to analyze for the presence of narrow
frequency band oscillations, as the following example demonstrates.

\begin{figure}
\epsscale{.80}
\plotone{white_red_compare.eps}
\caption{Comparison of the effect of assuming a white or red noise
  background on the detection of an oscillatory signal for simulated
  time-series.  Plot (a) shows the simulated time-series, generated
  from a \protect\PS\ \protect$P(f)\propto f^{-1.77}$ and no
  explicit oscillation included.  Plot (b) shows the wavelet power
  spectrum with the cone-of-influence (shaded area) and regions above
  the 95\% confidence level, assuming a white-noise (Gaussian)
 background .  Plot (c) shows the global wavelet \protect\PS\ for
  this wavelet transform.  Plots (d) and (e) are the same as plots (b)
  and (c) under the assumption of a red-noise background.}
\label{fig:comparison}
\end{figure}

Figure \ref{fig:comparison} shows how a red-noise \PS\ can be
mistakenly thought to contain an oscillatory signal.  The time series
(Figure \ref{fig:comparison}(a)) is constructed from a \PS\
$P(f)\approx f^{-1.77}$ with no explicit oscillatory content,
following the construction procedure of \cite{2010MNRAS.402..307V}.
Figure \ref{fig:comparison}(b) shows that the assumption of a
white-noise background and a 95\% confidence level leads to the
positive detection of significant oscillatory power in this time
series. Figure \ref{fig:comparison}(c) shows that the assumption of a
red-noise background with the same confidence level significantly
reduces the area for which a detection may be claimed.  Even with this
significantly different background assumption, there is still a
significant amount of wavelet power above the 95\% confidence level.
However, since the data is simulated without an explicit oscillatory
component, the high wavelet power must have arisen by chance.  The
simulated data, along with the results of Section \ref{sec:anal},
suggest that when examining the wavelet transforms of time-series for
wave packets, a background red-noise \PS\ should be assumed, along
with higher confidence levels (99\% or higher), in order to minimize
the effects of mistakenly identifying random variations in the
background \PS\ as evidence for an oscillatory signal.

However, even this approach to identifying oscillatory power is not
quite complete, as it simply rejects the null hypothesis that the
\PS\ can be adequately explained by a red-noise power
spectrum.  Model comparison techniques similar to that described in
Section \ref{sec:anal} are required to prefer a model with oscillatory
content over one without. The difficulty in finding narrow-band
features in Fourier power spectra against a red-noise background power
spectrum has been recognized by \cite{2010MNRAS.402..307V} in the
study of XMM-Newton observations of highly variable Seyfert 1
galaxies.  \cite{2010MNRAS.402..307V} presents a model fitting and
comparison technique that is directly applicable to the search for
oscillatory power in coronal time-series.

@@

Figure \ref{fig:compare171193} shows that time series from individual
pixels have power-law like power spectra.  This has implications for
the design of automated oscillation detection algorithms.  Such an
algorithm must take into account the nature of the \PS.
The power-law \PS\ itself lacks an easily definable
time-scale at or below which a background trend can be defined.
Automated detection algorithms that rely on background trend
subtraction such as \cite{2010SoPh..264..403I} must therefore look to
other reasons for to justify a time-scale.

@@

All the automated detection algorithms described above attempt to find
individual pixels that are obviously oscillating at some frequency,
using the strength of the oscillation at that frequency (compared to
some assumption of the background) as the key quantity to measure.
These pixels are then clumped together and the quality of the signal
is then assessed.  Detection algorithms based on {\it wave coherence},
such as \cite{2008SoPh..252..321M}, implement wave detection through
finding spatially contiguous regions of the corona which are coherent
in a given frequency range.  The frequency range searched is based on
previous experience.  Oscillations that are detected propagating along
loops are often found by considering distance-time plots
\citep{2000AA...355L..23D, 2003AA...404L...1K} and looking for
alternating brightening/darkening in those plots as a indicator of a
propagating wave.  This is essentially a coherence-based approach that
involves an implicit assessment of the likelihood that an oscillation
has been detected.  The basis of the assessment is a judgement that a
signal is seen in multiple contiguous pixels.  However, the results of
Section \ref{sec:anal} suggest that each pixel in these plots has a
red-noise background \PS: the discussion of Section
\ref{ssec:corseis} therefore suggests that the significance of any
claimed oscillation is much reduced.

\subsection{``Excess'' emission}\label{ssec:excess}
The models fits of Section \ref{sec:anal} indicate that equation
\ref{eqn:pwrlaw} is preferred over equation \ref{eqn:pwrlawbump} as
the superior description of the observed Fourier \PS. The
moss region shows the greatest contribution from the lognormal
distribution $G(\nu)$ over the background \PL.
\cite{2005ApJ...624L..61D} show that it is possible to leak
oscillatory power from lower in the atmosphere to the upper reaches of
the atmosphere through the simple expedient of tilting the field line.
This changes the acoustic cutoff frequency and so allows wave energy
to propagate up in to the upper atmosphere.  If spectral model $M_{2}$
represents conditions in the solar atmosphere, then it should be
possible to infer a distribution of field line angles with the solar
surface using \cite{2005ApJ...624L..61D} and the observed power
distribution $G(\nu)$.  This would constrain the distribution of field
line angles in the lower atmosphere in different regions of the solar
surface.

\subsection{Nature of the \protect\PL\ \protect\PS}\label{ssec:nplps}
The first contribution to both models $P_{0}$ and $P_{i}$ is a
red-noise like \PS.  It is present in both wavebands
studied and in all the regions, and so parsimony suggests that the
mechanism of its creation is both similar and ubiquitous in all parts
of the solar atmosphere.  We hypothesize that the \PL\ \PS\ is due to
the sum of a distribution of a large number of emission events having
different amounts of emission. \cite{2011soca.book.....A} describes how a
\PL\ \PS\ may obtained from such a distribution, and that argument is
outlined below.

Each emission event is modeled as an exponentially decaying function
of time $t$
\begin{equation}
\label{eqn:expdecay}
f(t) = \frac{E}{T}\exp\left(-\frac{t}{T}\right),
\end{equation}
for some timescale $T$ and emission $E$.  The corresponding \Fps\ is
\begin{equation}
\label{eqn:ftexpdecay}
P(\nu) = \frac{E}{1 + (2\pi \nu T)^{2}}.
\end{equation}
The total \Fps\ along the line of sight is given by
\begin{equation}
\label{eqn:sumftexpdecay}
P_{total}}(\nu) = \sum_{T}N(T)P_{T}(\nu)
\end{equation}
where $N(T)$ is the distribution of time-scales for all the events
along the line of sight.  Further, if the number of events of a given
emission $E$ is assumed to be
\begin{equation}
\label{eqn:energydistrib}
N(E) \propto E^{-\alpha_{E}}
\end{equation}
and the total emission in each event depends on its time scale $T$
such that
\begin{equation}
\label{eqn:energytime}
E \propto T^{1+\gamma}
\end{equation}
then it can be shown that the observed \PS\ can be
approximated by
\begin{equation}
\label{eqn:finalfps}
P_{total}(\nu) \propto \nu^{(2-\alpha_{E})(1+\gamma)}.
\end{equation}
This derivation shows it is possible to generate \PL\ power spectra
using swarms of statistically similar emission events.

This derivation of a \PL\ \PS\ shares many similar features
with the nanoflare model of {\it energy} deposition in the solar
atmosphere. In the nanoflare model,

However, inferring the properties of energy deposition events from the
observed emission \PL\ \PS\ depends strongly on three factors
that influence the observation.  Firstly, the distribution of events
along the line of sight and their temporal dependence (expressed
through the parameters $\alpha_{E}$ and $\gamma$ in Equation
\ref{eqn:energydistrib}) have strong effects on the observed \Fps.
Secondly, the energy radiated as a function of the energy deposited in
each event and the existing plasma properties must be consistently
modeled.  This is required to understand how much radiation at each
wavelength is emitted from the plasma.  This is a complex task to do
correctly, and there is much work ....

Finally, the AIA instrument
filters the emitted radiation, and this too must be modeled in order
to understand the observed \Fps.  These three features must be modeled
in order to test the hypothesis that ubiquitous energy deposition
events are the root cause of the observed power-law like behavior of
the Fourier power spectra.

@@

Time series of AIA 171\AA\ and 193\AA images show approximately power
law like properties over all regions of the solar surface.  Detecting
narrow band oscillatory power should take in to account the presence
of the \PL\ like \PS.  The power spectra have been
modelled using three components: a \PL\ \PS, a
lognormal component, and a constant background.  It is hypothesized
that the power-law component is due to the sum along the line of sight
of a large number of statistically similar energy deposition events.
It is also hypothesized that the lognormal component is due to the
channeling of oscillatory power from lower to higher levels of the
solar atmosphere.

@@

The estimated error in the estimated mean is
\begin{equation}
\sqrt{\hat{\sigma^{2}}}/\sqrt{N}
\label{eqn:errorsigmamean}
\end{equation}
where $N$ is the number of measurements taken.  This formula assumes
that the measurements taken are all independent of each other.
However, this is not the case for the Fourier power in any given
frequency.  This is because neighbouring pixels are highly likely to
be physically connected to each other, and so time-series in
neighboring pixels are likely to be strongly correlated (assuming that
the background structure exists over at least two pixels).  Secondly,
the point spread function of AIA spreads emission in one pixel over
its neighbors.  Therefore, the measurements used to generate an error
to the Fourier power are not independent.

Therefore, the number of effectively independent pixels is less than
the actual number of pixels used in any one region.  The number of
effective independent pixels is estimated in the following way.  The
cross correlation $c(\tau)$ function between two randomly chosen
next-nearest neighbor pixels is calculated.  The cross correlation
coefficient measures the linear dependence of two time series $X(t)$
and $Y(t \pm \tau)$ at different lags $\tau$.  This is used to define
a coefficient of independence between next nearest neighbor,
\begin{equation}
\label{eqn:ind}
\rho = 1 - \max|c(\tau)|.
\end{equation}
When $\rho$ is 1, the cross-correlation coefficient is zero, and there
is no measurable linear dependence between neighboring time series.
When $\rho$ is zero, the cross correlation coefficient is $\pm 1$, and
the two time-series are linearly dependent on each other.  The effect
number of independent pixels in region is given by
\begin{equation}
\label(eqn:nind}
N_{ind}= 1 + \rho(N_{pixel}-1)
\end{equation}
which is used in Equation \ref{eqn:errorsigmamean} to calculate the
estimated error in the mean.

@@

\bibliography{references}
\end{document}
However, other more complex models are certainly possible.  For
example, \cite{1993ASPC...42..111H} modelled the background
chromospheric Fourier \PS\ of a series of Ca-II K-line
images using a 19-parameter fit consisting of a constant background,
three components of the form
\begin{equation}
\label{eqn:harvey1}
P(\nu) \propto \frac{1}{1 + (2\pi \nu T_{0})^{b}}.
\end{equation}
and two components of the form
\begin{equation}
\label{eqn:harvey2}
P(\nu) \propto
\left(
\frac{\nu}{\nu_{0}}
\right)^{c}
\left(
\frac{\Gamma^{2}}{(\nu-\nu_{0})^{2} + \Gamma^{2}}
\right)^{b}.
\end{equation}

Finally, only two models of the Fourier \PS\ have been
considered.  The choice of equation \ref{eqn:pwrlaw} is motivated by
the observations of all four regions considered.  Equation
\ref{eqn:pwrlawbump} was motivated by previous observations of
oscillatory content in the solar atmosphere.  Equation
\ref{eqn:pwrlawbump} is shown to be the preferred model in all cases.
